%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{robertino-cv}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Robertino}{Martinez}{
\href{https://twitter.com/robertinom_en}{twitter.com/\_roberm\_} |
\href{https://github.com/IIPatternII}{github.com/rober-m} | \urlstyle{same}\href{https://robertinom.com}{robertinom.com} |
\href{mailto:robertinom@protonmail.com}{robertinom@protonmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.48\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work experience} 

\runsubsection{Educator}
\descript{| Input Output (IOG/IOHK) }
\location{2022-Present}
\begin{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Create and deliver courses, hackathons, and training about Haskell, Plutus, and other Cardano-related technologies.
\item Help to define best practices for smart contract development. 
\item Cardano developer advocate.
\end{tightemize}
\sectionsep

\runsubsection{ML Engineer}
\descript{| Government employee }
\location{2019-2020}
\begin{tightemize}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Hydrological and statistical analysis of the San Roque basin using Python and Pandas.
\item Development and assessment of an artificial neural network model capable of predicting the response of the basin and the level of the San Roque dam up to 6 months in advance (TensorFlow, Python, QGis).
\item Development of a web application to effortlessly use the AI model for decision-making about the dam's hydrologic resources (React, TensorFlow).
\end{tightemize}
\sectionsep

\runsubsection{Mobile app developer}
\descript{| Freelance }
\location{2017-2020}
\begin{tightemize}
\item Design and map out applications based on the needs and budget of the client.
\item Develop and test multi-platform applications (Android and iOS) using Flutter (Dart, Swift, Kotlin).
\item Provide tracking, quality control, and support to customers during and after product delivery.
\end{tightemize}
\sectionsep

\runsubsection{Researcher}
\descript{| Hydraulics and Hydrology Laboratory }
\location{2016-2017}
\begin{tightemize}
\item Collection and processing of hydrological data and generation of storm types (Python, R).
\item Creation of a program for digitalization and processing of pluviographic strips and statistical analysis of storms.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Formal Education}

\runsubsection{National Technological University}
\descript{| Civil Engineering (Argentina) }
\location{2012-2020}
\begin{tightemize}
\item Academic average: 8.3/10.
\end{tightemize}
\sectionsep

\runsubsection{Industrial Institute}
\descript{| Mid-level mechanical technician (High school) }
\location{2008-2011}
\sectionsep

\section{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.50\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ENTREPRENEURIAL EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Entrepreneurial Experience}

\runsubsection{Arquia}
\descript{| Co-Founder \& CTO }
\location{2021 - 2022}
The company develops multiple projects in multiple verticals using different technologies. I am solely responsible for the technological aspect and partly responsible for the economic and operational aspects.
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Design and develop cross-platform mobile applications (iOS and Android) using Flutter (Dart, Swift, Kotlin).
\item Design and develop back-ends using Firebase (database, auth, cron jobs, functions, etc.) and head-less WordPress (SQL, PHP). 
\item Design and develop Web applications.
\item Automation systems and DevOps (Python).
\item Setup and maintenance of virtual remote servers (CentOS and Ubuntu).
\item Analysis of usage data, market, competitors, and various metrics to optimize products, decision making, pivots, etc.
\item Directing all product efforts: deciding what features get built, when they are prioritized, and how they're launched.
\end{tightemize}
\sectionsep


\runsubsection{ClientFlows}
\descript{| Co-Founder }
\location{2021 – Present}
Client portal for small/medium businesses and freelancers (prelaunch).
\begin{tightemize}
\item Design and develop the Web platform using React.
\item Directing all product efforts (idem Arquia).
\item Directing all marketing and operational efforts: Profiling customers, campaigns, analysis of market trends, usage data, competitors, and other metrics related to decision-making.
\end{tightemize}
\sectionsep


\runsubsection{EBCourses}
\descript{| Founder }
\location{2020 – Present | \href{https://ebcourses.com/}{ebcourses.com} }
Platform that provides courses designed following scientific principles to maximize long-term retention.
\begin{tightemize}
\item Design and development of different courses consisting of theory, practice, and active recall exercises.
\item Design and development of an educational platform (React + Firebase + MailerLite API).
\item Directing all product efforts (idem Arquia) and directing all marketing and operational efforts (idem ClientFlows).
\end{tightemize}
\sectionsep


\runsubsection{SearchForMe}
\descript{| Founder }
\location{2020 – 2021 | \href{https://searchforme.app/}{searchforme.app}}
PDF reader with artificial intelligence capable of interpreting the contents, answering questions about said content, and showing the place where the answer is found.
\begin{tightemize}
\item Development of a PDF viewer desktop application with an ANN capable of interpreting questions and finding the answer inside the PDF's contents.
\item Directing all product efforts (idem Arquia) and directing all marketing and operational efforts (idem ClientFlows).
\end{tightemize}
\sectionsep


\end{minipage} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Skills} % It's at the end of previous column one.
\noindent\makebox[\linewidth]{\color{headings}\rule{\paperwidth}{0.4pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.48\textwidth} 


\subsection{Technical skills}
%\location{Proficient with:}
Blockchain \textbullet{}
Haskell \textbullet{}
Plutus \textbullet{}
Flutter \textbullet{}
Dart \textbullet{}
JavaScript \textbullet{}
TypeScript \textbullet{}
React \textbullet{}
Firebase \textbullet{}
Python \textbullet{}
Machine Learning %\textbullet{}
%Linux \textbullet{}
%HTML \textbullet{}
%CSS \textbullet{}
%Node.js 

%\location{Familiar with:}
%Blockchain \textbullet{}
%SQL\textbullet{}
%PHP \textbullet{}
%Haskell \textbullet{}
%Plutus
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.50\textwidth} 

\subsection{Soft skills}
%\location{Strong:}
Leadership \textbullet{}
Resourcefulness \textbullet{}
Initiative \textbullet{}
Bilingual Communication (English and Spanish) \textbullet{}
Pedagogy
\end{minipage} 

\sectionsep

\end{document}  \documentclass[]{article}
